Post MCMCglmm analyses

### 2021-04-28 Analysis/06-post_mcmcglmm_analyses.Rmd
Update 06-post_mcmcglmm_analyses.Rmd

```{r, eval = FALSE}
source("../Functions/vector.diff.R")
## Get all the angles and stuff
gull_results <- mapply(vector.diff, uncentered_major_axes$cladegulls, uncentered_major_axes$phylo)
plovers_results <- mapply(vector.diff, uncentered_major_axes$cladeplovers, uncentered_major_axes$phylo)
sandpipers_results <- mapply(vector.diff, uncentered_major_axes$cladesandpipers, uncentered_major_axes$phylo)

## Sort the results per type
angles <- cbind(gull_results["angle", ],
                plovers_results["angle", ],
                sandpipers_results["angle", ])
projections <- cbind(gull_results["projection", ],
                     plovers_results["projection", ],
                     sandpipers_results["projection", ])
rejections <- cbind(gull_results["rejection", ],
                    plovers_results["rejection", ],
                    sandpipers_results["rejection", ])
colnames(angles) <- colnames(projections) <- colnames(rejections) <- levels(morphdat$clade)
```

```{r, fig.height = 18, fig.heigh = 6, eval = FALSE}
## Plot the blob wise metrics
par(mfrow = c(3, 1))
boxplot(angles, col = colour_vector, ylab = "angle")
boxplot(projections, col = colour_vector, ylab = "projection (scaled)")
boxplot(rejections, col = colour_vector, ylab = "rejection (scaled)")
```

Same but with absolute values and angles modulo 90:

```{r, fig.height = 18, fig.heigh = 6, eval = FALSE}
## Plot the blob wise metrics
par(mfrow = c(3, 1))
boxplot(angles %% 90, col = colour_vector, ylab = "angle (modulo 90)")
boxplot(abs(projections), col = colour_vector, ylab = "projection (scaled - absolute)")
boxplot(abs(rejections), col = colour_vector, ylab = "rejection (scaled - absolute)")
```

@@

```{r, eval = FALSE}
library(dispRity)
## Wrapping function
lapply.projections <- function(one_axis, trait_space) {
    return(list(
        projection = projections(as.matrix(trait_space), point1 = one_axis[1,], point2 = one_axis[2,]),
        rejection  = projections(as.matrix(trait_space), point1 = one_axis[1,], point2 = one_axis[2,], measure = "distance")))
}
## Plot rejection/projection profiles
plot.proj.rej <- function(point_list, cols, data, main) {
    ## Colour vector
    colour_vector <- cols[morphdat$clade]
    colour_vector <- adjustcolor(colour_vector, alpha.f = 1/10)
    ## lims
    lim <- range(unlist(point_list))
    plot(NULL, xlim = lim, ylim = lim, xlab = "projection", ylab = "rejection", main = main)
    ## Add each points
    plot.points <- function(one_set, colour_vector) {
        points_args <- list()
        points_args$pch <- 19
        points_args$col <- colour_vector
        points_args$x <- one_set$projection
        points_args$y <- one_set$rejection
        do.call(points, points_args)
    }

    lapply(point_list, plot.points, colour_vector)
    return(invisible())
}

## Getting the results
phylo_results_uncentered <- lapply(uncentered_major_axes$phylogeny, lapply.projections, trait_space = morphdat[, c(1,2,3)])

## Plot results
plot.proj.rej(phylo_results_uncentered, cols = colour_vector, data = morphdat, main = "Phylo elaboration/rejection")
```

>>>>

```{r}
## Get all the angles and stuff
group_results <- analyses.group(uncentered_major_axes, base = "animal")
names(group_results) <- levels(morphdat$clade)
```

```{r, fig.height = 18, fig.heigh = 6}
## Plot the blob wise metrics
plot.analyses.group(group_results, col = colour_vector)
```

@@

```{r, eval = FALSE}
## Global per tip analyses
tip_results_global <- analyses.tip(data = morphdat, axes = uncentered_major_axes$phylogeny)

## Plot results
plot.analyses.tip(tip_results_global, cols = colour_vector, group = split(rownames(morphdat), f = morphdat$clade)))
```
